\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-30 OaklandSubmission/app-stash.tex
eval 6.1
intro related
minor

\divya{points that have to be there...} Security; traces are ``oblivious'' of secret values if observables/outputs are same; formal cryptographic security guarantee uses simulation paradigm \cite{canetti2000}

@@

>>>>

\divya{points that have to be there...} Security; traces are ``oblivious'' of secret values if observables/outputs are same; formal cryptographic security guarantee uses simulation paradigm

@@

\divya{references:} Lets cite CCS paper for Minionn and not eprint

\divya{experiments:} Should we do matrix factorization?

### 2017-10-30 OaklandSubmission/conclude.tex
minor

\section{Conclusion}
\label{sec:conclude}
\tool is the first
``cryptographic-cost aware'' framework that generates efficient and
scalable \mpc protocols from high-level programs.
The generated protocols comprise combinations
of arithmetic and boolean circuits and have performance comparable to
or better than the custom, specialized
protocols from previous works

>>>>

\section{Conclusion}
\label{sec:conclude}
\tool is the first
cryptographic-cost aware framework that generates efficient and
scalable \mpc protocols from high-level programs.
The generated protocols comprise combinations
of arithmetic and boolean circuits and have performance comparable to
or better than the custom, specialized
protocols from previous works.
